ComBatLS LBCC Results

### 2025-01-31 paper_lbcc_results.Rmd
figures

```{r}
demo_plt <- readRDS("figs/figure_5_AB.rds")

# study demographics
fig5_vert <- ggarrange(
#   #ggarrange(blank,
# ggarrange(sample_boxplot2, full_boxplot2,
#           sample_barplot2, full_barplot2,
#           nrow=2, ncol=2, 
#           #align = "v", 
#           common.legend = TRUE,
#           legend = "right",
#           widths=c(18, 1),
#           heights=c(1, 1)
#           ),
# blank,
# nrow=1, ncol=3,
# common.legend = FALSE,
# widths= c(1, 20, 1)),
# boxplots
demo_plt,
mean_cents_bxplt_nolabel,
common.legend=FALSE,
nrow=2, ncol=1,
heights=c(2, 1),
labels=c("", "C")
)

ggsave("figs/figure_5_vertical.jpeg", fig5_vert, width=17, height=15, units="in")
```

@@

mean_delta_fig <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=study_mean_age, y=abs_mean_delta_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = study_mean_age), data = pred_df1,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pred_df1, aes(y = fit, x=study_mean_age))+
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Mean Age of Primary Study Sample (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
#ggsave("figs/supp_mean_delta_fig.jpeg", mean_delta_fig, width=10, height=7, units="in")
```

@@

range_delta_fig <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=age_range, y=abs_mean_delta_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = age_range), data = pred_df2,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pred_df2, aes(y = fit, x=age_range))+
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Age Range of Primary Study Sample (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
```

@@

mean_delta_fig2 <- mean_cent_deltas_df_study %>%
  ggplot(aes(x=abs_age_diff, y=abs_mean_delta_cent)) +
  geom_point(alpha=0.05, aes(color=study)) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = abs_age_diff), data = pdat3,
                inherit.aes = FALSE, alpha = 0.4) +
    geom_line(data = pdat3, aes(y = fit, x=abs_age_diff)) +
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Subject's Offset from Mean Age of Primary Study (Years)", y="Mean Absolute Difference in Centile Scores (Centiles)")
#ggsave("figs/supp_mean_delta_fig2.jpeg", mean_delta_fig2, width=10, height=7, units="in")
```

>>>>

```{r}
demo_plt <- readRDS("figs/figure_5_A.rds")

# study demographics
fig5_vert <- ggarrange(
demo_plt,
mean_cents_bxplt_nolabel,
common.legend=FALSE,
nrow=2, ncol=1,
heights=c(1.3, 1),
labels="AUTO"
)
fig5_vert
ggsave("figs/figure_5_vertical.jpeg", fig5_vert, width=12, height=12, units="in")
```

@@

mean_delta_fig <- mean_cent_deltas_df_study %>%
  mutate(study = gsub("_", " ", study)) %>%
  ggplot(aes(x=study_mean_age, y=abs_mean_delta_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = study_mean_age), data = pred_df1,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pred_df1, aes(y = fit, x=study_mean_age))+
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Mean Age of Primary Study Sample (Years)", y="Mean Absolute Difference in Centiles",
       color="Study")
#ggsave("figs/supp_mean_delta_fig.jpeg", mean_delta_fig, width=10, height=7, units="in")
```

@@

range_delta_fig <- mean_cent_deltas_df_study %>%
  mutate(study = gsub("_", " ", study)) %>%
  ggplot(aes(x=age_range, y=abs_mean_delta_cent)) +
  geom_point(aes(color=study), alpha=0.2) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = age_range), data = pred_df2,
                inherit.aes = FALSE, alpha = 0.2) +
    geom_line(data = pred_df2, aes(y = fit, x=age_range))+
  theme_linedraw()+
  theme(legend.position="none") +
  labs(x="Age Range of Primary Study Sample (Years)", y="Mean Absolute Difference in Centiles")
```

@@

mean_delta_fig2 <- mean_cent_deltas_df_study %>%
  mutate(study = gsub("_", " ", study)) %>%
  ggplot(aes(x=abs_age_diff, y=abs_mean_delta_cent)) +
  geom_point(alpha=0.05, aes(color=study)) +
  geom_ribbon(aes(ymin = lower, ymax = upper,
                    x = abs_age_diff), data = pdat3,
                inherit.aes = FALSE, alpha = 0.4) +
    geom_line(data = pdat3, aes(y = fit, x=abs_age_diff)) +
  theme_linedraw()+
  labs(x="Subject's Offset from Mean Age of Primary Study (Years)", y="Mean Absolute Difference in Centiles",
       color="Study")

```

```{r}
sfig_lbcc <- ggarrange(
mean_delta_fig,
range_delta_fig,
mean_delta_fig2,
nrow=3, ncol=1,
labels="AUTO",
legend = "right",
common.legend=TRUE
)
sfig_lbcc
ggsave("figs/supp_lbcc.jpeg", sfig_lbcc, width=9, height=11, units="in")
```
